\begin{thebibliography}{20}
\bibitem{Swen} Robert Swendsen. An Introduction to Statistical Mechanics and Thermodynamics. Oxford University Press,  17.
\bibitem{Git} Github Repository: Chpel/ProjectMagnet (https://github.com/Chpel/ProjectMagnet)
\bibitem{NewBar} Newman, M. E. J. and Barkema, G. T.. Monte Carlo methods in statistical physics. Oxford: Clarendon Press, 1999.
\bibitem{Yanke} Janke W. Monte Carlo Methods in Classical Statistical Physics. In: Fehske H., Schneider R., Weiße A. (eds) Computational Many-Particle Physics. \emph{Lecture Notes in Physics, vol 739}. Springer, Berlin, Heidelberg, 2008.
\bibitem{Schro} Github Repository: Shroedingercat/Self-learning-Monte-carlo-algorithms (https://github.com/Shroedingercat/Self-learning-Monte-carlo-algorithms)
\bibitem{SAW} Github Repository: kamilla0503/SAWs (https://github.com/kamilla0503/SAWs)
\bibitem{saw} Github Repository: kamilla0503/saw (https://github.com/kamilla0503/saw)
\bibitem{Selke} Walter Selke. Critical Binder cumulant of two–dimensional Ising models. \emph{Eur. Phys. J. B}, 51(2):223-228, 2006.
\bibitem{Pelissetto} Sergio Caracciolo, Marco Gherardi, Mauro Papinutto, Andrea Pelissetto. Geometrical Properties of Two-Dimensional Interacting Self-Avoiding Walks at the $\theta$-point. \emph{J. Phys. A: Math. Theor.},44(11):1-24, 2011.
\bibitem{Janke_G} Handan Arkın and Wolfhard Janke. Gyration tensor based analysis of the shapes of polymer chains in an attractive spherical cage. \emph{J. Chem. Phys.} 138, 054904, 2013.
\bibitem{Foster} Damien Paul Foster and Debjyoti Majumdar. Critical behaviour of magnetic polymers in two and three dimensions. \emph{Phys. Rev. E}, 104:024122, Aug 2021.
\bibitem{Kamilla} Kamilla Faizullina, Ilya Pchelintsev, Evgeni Burovski. Critical and geometric properties of magnetic polymers across the globule-coil transition. \url{https://arxiv.org/abs/2107.11830}
\bibitem{Prellberg} Owzarek A. L. and Prellberg T. Scaling of the atmosphere of self-avoiding walks. \emph{J. Phys. A}, 41:375004, 2008.

\end{thebibliography}
